\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{times}
\usepackage{fontawesome}

% Set your name here
\def\name{Matthew C. McFee}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {chemical engineering, bioengineering, data analysis, biomedical engineering, data science, machine learning, computational science, computational biology},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \textbf{\name}}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.585\linewidth}
  \href{https://www.utoronto.ca/}{The University of Toronto} 
  \\ \href{http://ccbr.utoronto.ca/donnelly-centre-cellular-and-biomolecular-research}{The Donnelly Centre (Room 1140)}
  \\ 160 College St, Toronto, ON
  \\ M5S 3E1, Canada
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    \faPhone & 647-540-1388 \\
    \faEnvelope & \href{mailto:matthew.mcfee@mail.utoronto.ca}{matthew.mcfee@mail.utoronto.ca} \\
    \faLinkedinSquare & \href{https://www.linkedin.com/in/mattcmcfee}{https://www.linkedin.com/in/mattcmcfee}\\
    \faGithub & \href{https://github.com/allcatsaregrey}{https://www.github.com/allcatsaregrey}\\
    \faGlobe & \href{https://www.gilbert-lab.com/}{ https://www.gilbert-lab.com/} \\
    %\faGlobe & \href{https://www.kaggle.com/mattmcfee}{https://www.% kaggle.com/mattmcfee}
  \end{tabular}
\end{minipage}

\vspace{0.05in}

\noindent\makebox[\linewidth]{\rule{\textwidth}{2pt}} 

\section*{\textbf{Personal}}

\begin{itemize}
\item Date of Birth: January 11, 1994
\item Citizenship: Canadian
\item Languages: English (Fluent), Spanish (Basic)
\end{itemize}

\section*{\textbf{Education}}

\begin{itemize}
\item MASc Biomedical Engineering, The University of Toronto, September 2018 - December 2020 (Expected)
\end{itemize}

\begin{itemize}
  \item BASc Chemical and Biological Engineering, The University of British Columbia, September 2012 - April 2017
\end{itemize}

\section*{\textbf{Fellowships \& Awards}}
\begin{itemize}
    \item TOeP Fellowship, September 2018 - Present
    \item Barbara \& Frank Milligan Graduate Fellowship Award, 2018
\end{itemize}

\section*{\textbf{Additional Education \& Certifications}}

\begin{itemize}
    \item SciNet Data Science Certificate, June 2019 - July 2020 (Expected)
    \\The University of Toronto
    \\Toronto, ON
    \\Selected Courses: Neural Network Programming, Linux Shell Scripting, Machine Learning with Python, Introduction to Relational Databases
    %\item DataCamp Statement of Accomplishment, January 2020 - February 2020
    %\\Data Scientist with Python
    %\\Selected Courses: Data Manipulation with Pandas, Introduction to Data Visualization with Seaborn, Unsupervised Learning in Python, Cluster Analysis in Python
    %\item SciNet Summer School Certificate, June 2019
    %\\The University of Toronto
    %\\Toronto, ON
    %\\Advanced Linux, Python, Machine Learning
\end{itemize}

\section*{\textbf{Research Interests}}
\begin{itemize}
\item Computational biology, the applications of machine learning in biology and healthcare, modelling of biological processes/systems, bioengineering, biostatistics
%\item Machine learning, large scale data analysis, the application of machine learning to improve society
\end{itemize} 

\section*{\textbf{Research Experience}}

\subsection*{Graduate Thesis}
\begin{itemize}
    \item Adaption of a Muscle Endogenous Repair Assay for Industry and Academic Adoption (Supervisor: Dr. Penney Gilbert), September 2018 - December 2020 
\end{itemize}

\subsection*{Undergraduate Thesis}

\begin{itemize}
\item Derivation of Blood-Brain Barrier Cells from Induced Pluripotent Stem Cells and Blood Brain Barrier Formation Kinetics for the Testing of Penetrability of Anti-neurodegenerative Drugs (Supervisor: Dr. Vikramaditya G. Yadav), September 2015 - April 2017 
\end{itemize}

%\subsection*{Research Exchanges}
%\begin{itemize}
%\item Visiting Researcher, Laboratory of Quantitative Exercise Biology (Collaborator/Supervisor: Dr. David C. Clarke), Simon Fraser University, July 2020 - August 2020 
%\end{itemize}

\subsection*{Capstone Design Project}

\begin{itemize}
\item Anaerobic Digestion of Brewery Spent Grain for the Production of Bio-methane, September 2016 - April 2017
\\ Industry Advisors: Postmark Brewing, Quadrogen Power Systems Inc.
\end{itemize}

\section*{\textbf{Teaching Experience}}
\begin{itemize}
    \item BME1479 - Biostatistics, Winter 2020
    \\Institute of Biomaterials \& Biomedical Engineering
    \\The University  of Toronto
    \\Toronto, ON
    \\Instructor: Dr. Julie Audet PhD, P. Eng.
    \\Position: Teaching Assistant
    \item Bachelor of Education Practicum (Physics), Summer 2017
    \\ The University of British Columbia, Vancouver School Board
    \\ Vancouver, BC
    \\ Instructor/Supervisor: Mr. Adam Klaassen
    \\ Position: Teaching Assistant
\end{itemize}

\section*{\textbf{Professional Experience}}

\begin{itemize}
\item Boston Scientific, March 2018 - June 2018
\\Vancouver, BC
\\Position: Manufacturing Associate (track to Manufacturing Engineer)
\end{itemize}

\section*{\textbf{Journal Articles}}

In progress:
\begin{enumerate}
\item A. Fard*, \textbf{M. McFee*}, E. Jacques, S. Davoudi, B. Xu, A.P. McGuigan \& P.M. Gilbert, "Muscle endogenous repair assay adaptions for industry and academic adoption", in preparation for submission
\end{enumerate}

Submitted:
\begin{enumerate}
\item B. Xu*, S. Davoudi*, J.L. Cardenas, \textbf{M. McFee}, E. Jacques, C.Y. Chin, A. Fard, M. Ebrahimi, M.A. Bakooshli, R. Marcellus, K. Tung, H. Ahn, H.J. Ginsberg, A.P. McGuigan \& P.M. Gilbert, "An in vitro functional assay to predict in vivo muscle stem cell mediated repair", submitted to Nature Biotechnology (May 2020)

\item S. Barsky, A. Govette, M. Holowaty, L. O'Brien,  \textbf{M. McFee}, M.A. Bakooshli \& D. Moore, "(Run) Over the hill: exercising to prevent age-related denervation", submitted to Journal of Physiology (April 2020)
%\item R. Vaez Ghaemi, M. McFee \& V. G. Yadav, "Exploration of Novel Materials for Studying Cell Deposition and Tissue Assemblage", submitted to Langmuir
\end{enumerate}

Published:
\begin{enumerate}
    \item R. Vaez Ghaemi, I. L. Co, \textbf{M. McFee} \& V. G. Yadav, "Brain organoids: An engineered solution for addressing neuroscience's grandest challenges", published by Advanced Biosystems (October 2018)
    
    {\tiny Note: * indicates equal contribution to authorship.}
\end{enumerate}



\section*{\textbf{Conferences \& Seminars}}

\begin{itemize}
\item June 2020 \textbf{Oral Presentation.} "Making muscle! How we build miniature muscles to test repair enhancing drugs." The University of Toronto Engineering Research Conference (UTERC). Toronto, ON
\item May 2020 \textbf{Abstract Presentation.} "Adaping a Novel Muscle Endogenous Repair Assay For Industry and Academic Adoption" Muscle Health Awareness Day (YorkU). Toronto, ON
\item December 2019 \textbf{Student Seminar.} "MEndR Adaptions to Facilitate Industry and Academic Adoption" Institute of Biomaterials \& Biomedical Engineering Student Seminar Series. Toronto, ON
\href{https://bcregmed.ca/wp-content/uploads/2018/05/BCRegMed-Symposium-Abstract-Booklet_May-9-2018_Final.pdf}{\item May 2018 \textbf{Poster Presentation.} "Brain organoids: A transformative, new research tool for neuroscience research" BCRegMed Symposium. Vancouver, BC}
 \href{https://biomaterials.ca/static/abstracts/view/114124}{\item May 2017 \textbf{Poster Presentation.} "Towards Layer-by-layer Manufacturing of Engineered Tissues" Canadian Biomaterials Society Conference. Winnipeg, MB}
\item March 2017 \textbf{Poster Presentation.} "Engineering Cerebroids for the Testing of Anti-neurodegeneration Drugs" AICHe Pacific Northwest Regional Conference. Corvalis, OR
\end{itemize}

\section*{\textbf{Volunteering \& Mentorship}}
\begin{itemize}
    \item Graduate \& Life Sciences Education Shadowing Program, February 2019 - July 2019
    \\The University of Toronto
    \\Toronto, ON
    \\Position: Graduate Mentor 
    \item The University of Toronto Skule Alumni Mentorship Program, 2019
    \\Toronto, ON
    \\Position: Student Mentee
    \\Mentor: Dr. Adam Grossman, PhD (Data Scientist)
    \\Company: Praedicat 
\end{itemize}

\section*{\textbf{Entrepreneurial \& Additional Professional Experience}}

\begin{itemize}
\item H. Lorenzo, August 2015 - December 2017
\\Los Angeles, CA
\\Position: Seasonal Model and Stylist
\\Highlights: \href{https://www.highsnobiety.com/2016/09/10/raf-simons-fw16-collection-h-lorenzo-editorial/}{Raf Simons FW16}, \href{https://hypebeast.com/2017/12/julius-spring-summer-2018-collection-h-lorenzo-pop-up}{JULIUS SS17}, \href{https://hypebeast.com/2018/1/not-applicable-selfridges-michele-lamy}{N/A x Selfridges "Lamyland"}
\item BAD BOY, January 2017 - March 2017
\\Vancouver, BC
\\Position: Co-founder, Model, and Sales
\\{\tiny Notes: (1) Name change to "Stranger Showroom." (2) Closed as of March 2019 (3) Currently operating as of May 2020}
\end{itemize}

%\section*{Programming Languages \& Relevant Software}
%\begin{itemize}
%\item Python (Data Science, machine Learning, general purpose)
%\item R (Data visualization, statistical analysis)
%\item C (General purpose)
%\item \LaTeX
%\item JMP 
%\item ImageJ
%\end{itemize}

\section*{\textbf{Programming Languages \& Software}}
\begin{itemize}
    \item \textit{Languages:} \textbf{Python}, \textbf{R}, C, MATLAB, \LaTeX, (R)Markdown, ImageJ Macro Language
    \item \textit{Software:} Emacs, Bash, Git, ImageJ, JMP, Inkscape, GraphPad Prism, PostgreSQL, Aspen Plus
    \item \textit{Libraries:} Pandas, NumPy, SciPy, scikit-learn, scikit-image, TensorFlow, Keras, Seaborn, OpenCV, ggplot2, tidyverse, org-mode
    \item \textit{Operating Systems}: Fedora, CentOS GNU/Linux, FreeBSD\\\\
    \tiny{Note: Bolded languages are those with which I have the most experience}
\end{itemize}

\section*{\textbf{Recreational Interests}}
\begin{itemize}
\item Powerlifting, heavy metal music, fashion design, learning about mathematics, statistics and programming, watching horror films (Fulci and Carpenter are favourites)
\end{itemize}

\section*{\textbf{References}}

\begin{multicols}{3}
\begin{itemize}
    \item Dr. Penney Gilbert, PhD
    \\Relationship: Thesis Advisor
    \\\faPhone & 416-978-2501
    \\\faEnvelope & \href{mailto: penney.gilbert@mail.utoronto.ca}{penney.gilbert@utoronto.ca}
    \item Dr. Alison McGuigan, PhD
    \\Relationship: Research collaborator, Co-author
    \\\faPhone & 416-978-7552
    \\\faEnvelope & \href{mailto:alison.mcguigan@utoronto.ca}{alison.mcguigan@utoronto.ca}
     \item Dr. Julie Audet, PhD, P. Eng.
    \\Relationship: Course Instructor
    \\\faPhone & 416-978-1713
    \\\faEnvelope & \href{mailto:julie.audet@utoronto.ca}{julie.audet@utoronto.ca}
    %\item Dr. Daniel Moore, PhD
    %\\Relationship: Instructor, Co-author
    %\\\faPhone & 416-946-4088
    %\\\faEnvelope & %\href{mailto:dr.moore@utoronto.ca}{dr.moore@utoronto.ca}
\end{itemize}
\end{multicols}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \faPhone & 647-540-1388 \\
    \faEnvelope & \href{mailto:matthew.mcfee@mail.utoronto.ca}{matthew.mcfee@mail.utoronto.ca} \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}